### 2015-11-23 ms/ms_probaweb.tex
Minor edits

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Tomas Roslin$^{6}$, Tommy Nyman$^{6}$, Ben Baiser$^{7}$, Daniel B. Stouffer$^{3}$ \\

@@

>>>>

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, N\'eo
Martinez$^{5}$, Tommy Nyman$^{6}$, Timoth\'ee Poisot$^{2,7}$, Tomas Roslin$^{6}$, Spencer Wood$^{8}$, Daniel B. Stouffer$^{9}$, Jason Tylianakis$^{9}$\\

@@

8:\\

9:\\
